---
title: Reset seed status
output: html_document
params:
  flexTeaching_pars:
    value:
      solutions: true
  flexTeaching:
    value:
      menu: Reset seed status
      seed_salt: 8r0wlf55o486dv85v8fy
      data_salt: qt2egamos21mt8iv2kbr
      hide_before: 10:13 2023-03-28
      restrict_before: 10:13 2023-03-28
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE
  , dev = "png"
  , dpi = 300
  , out.width = ifelse(knitr::is_latex_output(), '.8\\linewidth', '80%')
  )

# For convenience; we use this options template to flag solutions blocks
knitr::opts_template$set(solutions = list(
  eval    = params$flexTeaching_pars$solutions, 
  include = params$flexTeaching_pars$solutions
  )
)

```

`flexTeaching3` is (in part) a random seed management software; given the inputs from the interface, it creates a unique seed and serves a document that is based on that unique random seed. Every time we run the same assignment with the same seed, we should get the same result.

The introduction of conditionally-evaluated code chunks, however, complicates this. When we request the solutions, generally, there will be some code chunks that will be run that *would not* have been run if we did not request the solutions. This is good; it allows the assignments without solutions to be served faster because not everything has to be computed until we request the solutions.

If we were to sample random numbers --- or run any function that samples random numbers in background, even unbeknownst to us --- in a solutions chunk, then the random seed for any *later* samples will be different from if we hadn't run that solutions chunk, because the random seed is changed after every sample. This would be potentially disastrous; any solutions might not be correct.

```{r fig.cap="How including an intervening chunk can change the random seed state, assuming its code uses the random number generator somehow."}
DiagrammeR::grViz(diagram = 'gv/seeds.gv',width = 700, height=500) 
```

There are several ways around this:

* **Do not sample in conditionally-evaluated blocks**, and only sample *before* any conditionally-evaluated blocks. For instance, generate any random data that will be downloaded by students in a setup block before all other content.
* Use a special hook in the `flexTeaching.api` package to **reset the random seed** after the chunk is done running.
* **Always generate random chunks; display them only when needed**. If the random chunks are always executed, then every chunk will always have the same random state. This is undesireable, though, in situations where the optional chunks take time to execute.

## Resetting the random seed


### Block 1

```{r}
rnorm(1)
```


```{r opts.label='solutions', child="children/solutions1.Rmd", ft3_seed_status="reset"}
```

### Block 2

```{r}
rnorm(1)
```


## Running chunks but not including them

We can also execute solution chunks, but not *include* them when we're not showing the solutions. This has the downside of running unnecessary code, which may be time consuming.

### Block 3

```{r}
rnorm(1)
```


```{r include = params$flexTeaching_pars$solutions, results='asis'}
## The "include" option is incompatible with the "child" option, 
## so we use knit_child and 'asis' output instead.
knitr::knit_child(
  "children/solutions2.Rmd",
  quiet=TRUE,
  envir = environment() # include the current environment
  ) |>
  cat()
```

### Block 4

```{r}
rnorm(1)
```


## The wrong way: showing the problem

### Block 5

```{r}
rnorm(1)
```


```{r opts.label='solutions', child="children/solutions3.Rmd"}
```

### Block 6

The random number below will have a value that depends on whether solutions are displayed. 

```{r }
rnorm(1)
```


