---
title: Using the import package
output: html_fragment
params:
  flexTeaching_pars:
    value:
      solutions: true
  flexTeaching:
    value:
      menu: Using the import package
      seed_salt: z5xbidx79xrwq8tw6x0az
      data_salt: a038ef1vp2s4vj2cyn58b
      hide_before: 10:13 2023-03-28
      restrict_before: 10:13 2023-03-28
      use_callr: false
      files:
        assignment_data.csv:
          label: Data
          icon: 'fa-solid fa-lg fa-file'
          filename: flexTeaching3.api::ft3_create_filename
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE
  , dev = "png"
  , dpi = 300
  , out.width = ifelse(knitr::is_latex_output(), '.8\\linewidth', '80%')
  )

# For convenience; we use this options template to flag solutions blocks
knitr::opts_template$set(solutions = list(
  eval    = params$flexTeaching_pars$solutions, 
  include = params$flexTeaching_pars$solutions
  )
)

# Replace this with your random data; it will be served if you 
# keep the files: settings in the YAML header
my_data = sleep
write.csv(my_data, 'assignment_data.csv', row.names = FALSE)

```

**To see the slow-down from using `callr`, see the "Using the import package (using callr)" assignment.**

Two things can make document compilation slow: rendering a full document (e.g., with `html_document` instead of `html_fragment`) and the default use of the [`callr`](https://callr.r-lib.org/) package to render documents in their own R process. The use of `callr` is for safety: the compilation of the document cannot affect the main R process if everything is compiled in a separate process. This slows compilation down, but makes it safer.

It is possible to speed things up by using the `flexTeaching3` setting `use_callr: false`. This comes with dangers. Loading the `dplyr` package with `library()`, for instance, will mask the base R function `stats::filter()` with its own `dplyr::filter()` function, potentially causing conflicts with other code.

The [`import`](https://cran.r-project.org/web/packages/import/vignettes/import.html) package allows us to easily use package functions without using `library()`. Instead of always referring to functions using the colon operator `::` (which is tedious), we can "import" functions from a package:

```{r echo=TRUE}
import::here(`%>%`, mutate, filter, select, summarise, group_by, n, .from = dplyr)

# We can now use these dplyr functions
my_data %>%
  group_by(group) %>%
  summarise(
    n    = n(),
    mean = mean(extra),
    se   = sd(extra)/sqrt(n)
    ) -> summaries

import::here(kbl, kable_styling, .from='kableExtra')

summaries |>
  kbl() |>
  kable_styling()
```

This will only solve one potential problem use turning off `callr` for an assignment; you also have to be cautious of [non-thread-safe code](https://github.com/rexyai/RestRserve/issues/195#issuecomment-1312577727). 

```{r opts.label='solutions', out.width='50%'}
# We can also import all functions
import::here(ggplot2, .all=TRUE)

summaries |>
  ggplot(aes(x = group, y = mean)) +
  geom_point(shape = 19) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width=0)

```





